---
title: "Buoy Project"
author: "Haoran Su, Haoyu Li, Xijia Luo, Yifan Liu"
date: "2020/9/24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(tidyverse)
library(stringr)
library(tidyr)
library(lubridate)
library(arm)
library(ggplot2)
library(dplyr)
library(forcats)
library(lme4)
library(purrr)
library(readr)
library(tibble)
```

# Introduction

Over the past 50 years, the average global temperature has increased at the fastest rate in recorded history. Scientists agree that the earth's rising temperatures are fueling longer and hotter heat waves, more frequent droughts, heavier rainfall, and more powerful hurricanes. On the other hand, the earth's ocean temperatures are getting warmer, too. Thus, it is important for us to monitor the ocean temperatures with buoys. A buoy is a floating device equipped to measure weather parameters. It might be anchored or allowed to drift in the open ocean currents. This report using data gathered from the National Oceanic and Atmospheric Administration's National Data Buoy Center. The purpose of this report is to explore the factors that might influence the air temperature (ATMP) above the sea level. 

## Import Data
```{r}

#1999
Buoy1999<-read.csv("1999.txt",sep="",header = T)
Buoy1999$TIDE<-0
Buoy1999$mm<-0
colnames(Buoy1999)[1]<-"X.YY"
colnames(Buoy1999)[5]<-"WDIR"
colnames(Buoy1999)[12]<-"PRES"

#2000
Buoy2000<-read.csv("2000.txt",sep="",header = T)
Buoy2000$TIDE<-0
Buoy2000$mm<-0
colnames(Buoy2000)[1]<-"X.YY"
colnames(Buoy2000)[5]<-"WDIR"
colnames(Buoy2000)[12]<-"PRES"

#2001
Buoy2001<-read.csv("2001.txt",sep="",header = T)
Buoy2001$mm<-0
colnames(Buoy2001)[1]<-"X.YY"
colnames(Buoy2001)[5]<-"WDIR"
colnames(Buoy2001)[12]<-"PRES"


#2002
Buoy2002<-read.csv("2002.txt",sep="",header = T)
Buoy2002$mm<-0
colnames(Buoy2002)[1]<-"X.YY"
colnames(Buoy2002)[5]<-"WDIR"
colnames(Buoy2002)[12]<-"PRES"

#2003
Buoy2003<-read.csv("2003.txt",sep="",header = T)
Buoy2003$mm<-0
colnames(Buoy2003)[1]<-"X.YY"
colnames(Buoy2003)[5]<-"WDIR"
colnames(Buoy2003)[12]<-"PRES"

#2004
Buoy2004<-read.csv("2004.txt",sep="",header = T)
Buoy2004$mm<-0
colnames(Buoy2004)[1]<-"X.YY"
colnames(Buoy2004)[5]<-"WDIR"
colnames(Buoy2004)[12]<-"PRES"

#2005
Buoy2005<-read.csv("2005.txt",sep="",header = T)
mm2005<-Buoy2005$mm
Buoy2005$mm<-NULL
Buoy2005$mm<-mm2005
colnames(Buoy2005)[1]<-"X.YY"
colnames(Buoy2005)[5]<-"WDIR"
colnames(Buoy2005)[12]<-"PRES"

#2006
Buoy2006<-read.csv("2006.txt",sep="",header = T)
mm2006<-Buoy2006$mm
Buoy2006$mm<-NULL
Buoy2006$mm<-mm2006
colnames(Buoy2006)[1]<-"X.YY"
colnames(Buoy2006)[5]<-"WDIR"
colnames(Buoy2006)[12]<-"PRES"

#2007
Buoy2007<-read.csv("2007.txt",sep="",header = T)
mm2007<-Buoy2007$mm
Buoy2007$mm<-NULL
Buoy2007$mm<-mm2007
Buoy2007 = Buoy2007[-c(1),]

#2008
Buoy2008<-read.csv("2008.txt",sep="",header = T)
mm2008<-Buoy2008$mm
Buoy2008$mm<-NULL
Buoy2008$mm<-mm2008
Buoy2008 = Buoy2008[-c(1),]


#2009
Buoy2009<-read.csv("2009.txt",sep="",header = T)
mm2009<-Buoy2009$mm
Buoy2009$mm<-NULL
Buoy2009$mm<-mm2009
Buoy2009 = Buoy2009[-c(1),]

#2010
Buoy2010<-read.csv("2010.txt",sep="",header = T)
mm2010<-Buoy2010$mm
Buoy2010$mm<-NULL
Buoy2010$mm<-mm2010
Buoy2010 = Buoy2010[-c(1),]

#2011
Buoy2011<-read.csv("2011.txt",sep="",header = T)
mm2011<-Buoy2011$mm
Buoy2011$mm<-NULL
Buoy2011$mm<-mm2011
Buoy2011 = Buoy2011[-c(1),]

#2012
Buoy2012<-read.csv("2012.txt",sep="",header = T)
mm2012<-Buoy2012$mm
Buoy2012$mm<-NULL
Buoy2012$mm<-mm2012
Buoy2012 = Buoy2012[-c(1),]

#2013
Buoy2013<-read.csv("2013.txt",sep="",header = T)
mm2013<-Buoy2013$mm
Buoy2013$mm<-NULL
Buoy2013$mm<-mm2013
Buoy2013 = Buoy2013[-c(1),]

#2014
Buoy2014<-read.csv("2014.txt",sep="",header = T)
mm2014<-Buoy2014$mm
Buoy2014$mm<-NULL
Buoy2014$mm<-mm2014
Buoy2014 = Buoy2014[-c(1),]

#2015
Buoy2015<-read.csv("2015.txt",sep="",header = T)
mm2015<-Buoy2015$mm
Buoy2015$mm<-NULL
Buoy2015$mm<-mm2015
Buoy2015 = Buoy2015[-c(1),]

#2016
Buoy2016<-read.csv("2016.txt",sep="",header = T)
mm2016<-Buoy2016$mm
Buoy2016$mm<-NULL
Buoy2016$mm<-mm2016
Buoy2016 = Buoy2016[-c(1),]

#2017
Buoy2017<-read.csv("2017.txt",sep="",header = T)
mm2017<-Buoy2017$mm
Buoy2017$mm<-NULL
Buoy2017$mm<-mm2017
Buoy2017 = Buoy2017[-c(1),]

#2018
Buoy2018<-read.csv("2018.txt",sep="",header = T)
mm2018<-Buoy2018$mm
Buoy2018$mm<-NULL
Buoy2018$mm<-mm2018
Buoy2018 = Buoy2018[-c(1),]

#2019
Buoy2019<-read.csv("2019.txt",sep="",header = T)
mm2019<-Buoy2019$mm
Buoy2019$mm<-NULL
Buoy2019$mm<-mm2019
Buoy2019 = Buoy2019[-c(1),]

#Combine

Buoy<-rbind(Buoy1999,Buoy2000,Buoy2001,Buoy2002,Buoy2003,Buoy2004,Buoy2005,Buoy2006,Buoy2007,Buoy2008,Buoy2009,Buoy2010,Buoy2011,Buoy2012,Buoy2013,Buoy2014,Buoy2015,Buoy2016,Buoy2017,Buoy2018,Buoy2019)
```

## Data Clean
```{r}
Buoy2 = filter(Buoy, hh == 10)
Buoy2 = data.frame(sapply(Buoy2, as.numeric))
Buoy2[Buoy2==99|Buoy2==999|Buoy2==9999]<-0
Buoy2$date <- make_datetime(Buoy2$X.YY,Buoy2$MM,Buoy2$DD)

```

## model
```{r}
set.seed(10000)
fit = lm(ATMP~WDIR+WSPD+GST+WVHT+DPD+APD+MWD+PRES+WTMP, data = Buoy2)
summary(fit)
```
```{r}
par(mfrow=c(2,2))
plot(fit)
```

## plot
```{r}
ggplot(data=Buoy2, aes(x=date, y=ATMP)) + geom_line() + xlab("")
```
```{r}
ggplot(data=Buoy2, aes(x=WTMP, y=ATMP)) + geom_point()
```

##  CONSIDERATIONS(curiosity)

There are several additional considerations to help to fully understand this study. Firstly, our data sources are very limited since all these data come from the same observation station(44013). To make our conclusion and model more reliable, we need to collect data from more stations in different locations such as in the west American or in Eurasia. Secondly, we don't have not enough time span on our data. We think 20 year is not enough to make an accurate conclusion or prediction on ATMP above sea level. 

